---
title: "Assignment-Modeling"
author: "Shary Beshara"
date: "April 14, 2016"
output: html_document
---


```{r message=FALSE}
library(dplyr)
library(RWeka)
library(knitr)
```

##1. Loading sonar data:
```{r}
sonar <- read.csv("~/Desktop/sonar.all-data.csv", header=FALSE)
```

##2.1 Constructing a C4.5 decision tree using the entire dataset
```{r}
fit <- J48(V61~., data=sonar)
```

Getting summary of training:
```{r}
c4.5_summary <- summary(fit) 
c4.5_summary
```

Create Map of measrures:
```{r}
measuresMap <- function(classifier){
  map <- new.env(hash=T, parent=emptyenv())
  map[["TM"]] <- classifier$confusionMatrix[1, 1]
  map[["TR"]] <- classifier$confusionMatrix[2, 2]
  map[["FM"]] <- classifier$confusionMatrix[2,1]
  map[["FR"]] <- classifier$confusionMatrix[1,2]
  map[["Accuracy"]] <- (map[["TM"]] + map[["TR"]]) /(map[["TM"]] + map[["TR"]] +     map[["FM"]] + map[["FR"]])
  map[["Error_rate"]] <- 1 - map[["Accuracy"]]
  map[["Precision"]]  <- map[["TM"]] / (map[["TM"]] + map[["FM"]])
  map[["Recall"]]  <- map[["TM"]] / (map[["TM"]] + map[["FR"]])
  map[["F-score"]]  <- 2 * (map[["Precision"]] * map[["Recall"]] /(map[["Precision"]] + map[["Recall"]]))
  return (map)
}
```

Calculating classification evaluation measures:
```{r}
c4.5 <- measuresMap(c4.5_summary)
cat("Accuracy = ", c4.5[["Accuracy"]], ", Error rate = ", c4.5[["Error_rate"]], ", Precision = ", c4.5[["Precision"]], ", Recall = ", c4.5[["Recall"]], ", F-score = ", c4.5[["F-score"]])
```
We can notice the over-fitting because the training and testing of the classifier are done with the same dataset.

##2.2 Testing C4.5classifier using a 10-fold cross-validation:
```{r}
C4.5CV <- evaluate_Weka_classifier(fit, numFolds = 10)
C4.5CV
```
  
Calculating classification evaluation measures:
```{r}
c4.5_cv <- measuresMap(C4.5CV)
cat("Accuracy = ", c4.5_cv[["Accuracy"]], ", Error rate = ", c4.5_cv[["Error_rate"]], ", Precision = ", c4.5_cv[["Precision"]], ", Recall = ", c4.5_cv[["Recall"]], ", F-score = ", c4.5_cv[["F-score"]])
```
#####This shows the improvement of the results as 10-fold cross validation divide the data into two groups one for training and the other one for testing which is repeated for 10 times

##3.1 Other classification algorithms: 
Random Forest
```{r}
RF <- make_Weka_classifier("weka/classifiers/trees/RandomForest")
randomForest <- RF(V61~., data=sonar) %>% evaluate_Weka_classifier(numFolds = 10)
randomForest
rf <- measuresMap(randomForest)
cat("Accuracy = ", rf[["Accuracy"]], ", Error rate = ", rf[["Error_rate"]], ", Precision = ", rf[["Precision"]], ", Recall = ", rf[["Recall"]], ", F-score = ", rf[["F-score"]])
```

SVM
```{r}
SVM = SMO(V61~., data=sonar) %>% evaluate_Weka_classifier(numFolds = 10)
SVM
svm <- measuresMap(SVM)
cat("Accuracy = ", svm[["Accuracy"]], ", Error rate = ", svm[["Error_rate"]], ", Precision = ", svm[["Precision"]], ", Recall = ", svm[["Recall"]], ", F-score = ", svm[["F-score"]])
```

Naive Bayes
```{r}
NB <- make_Weka_classifier("weka/classifiers/bayes/NaiveBayes")
naiveBayes<- NB(V61~., data=sonar) %>% evaluate_Weka_classifier( numFolds = 10)
naiveBayes
nb <- measuresMap(naiveBayes)
cat("Accuracy = ", nb[["Accuracy"]], ", Error rate = ", nb[["Error_rate"]], ", Precision = ", nb[["Precision"]], ", Recall = ", nb[["Recall"]], ", F-score = ", nb[["F-score"]])
```

Neural Networks
```{r}
#NN <- make_Weka_classifier("weka/classifiers/functions/MultilayerPerceptron")
#neuralNetwork<- NN(V61~., data=sonar) %>% evaluate_Weka_classifier( numFolds = 10)
#neuralNetwork
#nn <- measuresMap(neuralNetwork)
#cat("Accuracy = ", nn[["Accuracy"]], ", Error rate = ", nn[["Error_rate"]], ", Precision = ", nn[["Precision"]], ", Recall = ", nn[["Recall"]], ", F-score = ", nn[["F-score"]])
```

Bagging:
```{r}
BAG = Bagging(V61~., data=sonar, control = Weka_control(W = J48)) %>% evaluate_Weka_classifier(numFolds = 10)
BAG
bag <- measuresMap(BAG)
cat("Accuracy = ", bag[["Accuracy"]], ", Error rate = ", bag[["Error_rate"]], ", Precision = ", bag[["Precision"]], ", Recall = ", bag[["Recall"]], ", F-score = ", bag[["F-score"]])
```

Boosting:
```{r}
BOOST = AdaBoostM1(V61~., data=sonar, control = Weka_control(W = J48)) %>% evaluate_Weka_classifier(numFolds = 10)
BOOST
boost <- measuresMap(BOOST)
cat("Accuracy = ", boost[["Accuracy"]], ", Error rate = ", boost[["Error_rate"]], ", Precision = ", boost[["Precision"]], ", Recall = ", boost[["Recall"]], ", F-score = ", boost[["F-score"]])
```

##3.2 Compare between Bagging, Boosting and C4.5:
```{r}
cat("C4.5 measures:"," Accuracy = ", c4.5_cv[["Accuracy"]], ", Error rate = ", c4.5_cv[["Error_rate"]], ", Precision = ", c4.5_cv[["Precision"]], ", Recall = ", c4.5_cv[["Recall"]], ", F-score = ", c4.5_cv[["F-score"]])
cat("Bagging measures:","Accuracy = ", bag[["Accuracy"]], ", Error rate = ", bag[["Error_rate"]], ", Precision = ", bag[["Precision"]], ", Recall = ", bag[["Recall"]], ", F-score = ", bag[["F-score"]])
cat("Boosting measures:", " Accuracy = ", boost[["Accuracy"]], ", Error rate = ", boost[["Error_rate"]], ", Precision = ", boost[["Precision"]], ", Recall = ", boost[["Recall"]], ", F-score = ", boost[["F-score"]])
```
So as expected we can see from the result that all the measures are better in bagging and boosting than in C4.5 classifier.

##4.1.1 Loading new datasets
Loading hepatitis data:
```{r}
hepa <- read.csv("~/Downloads/hepatitis.data.txt", header=FALSE)
hepa$V1 <- as.factor(hepa$V1)
```

Loading spect data:
```{r}
spect.train <- read.csv("~/Downloads/SPECT.train.txt", header=FALSE)
spect.test <- read.csv("~/Downloads/SPECT.test.txt", header=FALSE)
spect <- rbind(spect.test, spect.train)
spect$V1 <- as.factor(spect$V1)
```

Loading diabetes data:
```{r}
diabetes <- read.csv("~/Downloads/pima-indians-diabetes.data.txt", header=FALSE)
diabetes$V9 <- as.factor(diabetes$V9)
```

Forming one function for each dataset: 
```{r}
sonarClassification <- function(c){
  l <- list()
  accuracy <- 0
  error_rate <- 0
  precision <- 0
  recall <- 0
  f <- 0
  all_a <- list()
  all_p <- list()
  all_r <- list()
  all_f <- list()
  for(i in 1:10){
    classifier <- c(V61~., data=sonar) %>% evaluate_Weka_classifier(numFolds = 10)
    l[[i]] <- measuresMap(classifier)
    all_a[[i]] <- l[[i]][["Accuracy"]]
    all_p[[i]] <- l[[i]][["Precision"]]
    all_r[[i]] <- l[[i]][["Recall"]]
    all_f[[i]] <- l[[i]][["F-score"]]
    accuracy <- accuracy + l[[i]][["Accuracy"]]
    error_rate <- error_rate + l[[i]][["Error_rate"]]
    precision <- precision + l[[i]][["Precision"]]
    recall <- recall + l[[i]][["Recall"]]
    f <- f + l[[i]][["F-score"]]
  }
  map <- new.env(hash=T, parent=emptyenv())
  map[["Accuracy"]] <- accuracy /10
  map[["Error_rate"]] <- error_rate/10
  map[["Precision"]]  <- precision/10
  map[["Recall"]]  <- recall/10
  map[["F-score"]]  <-f/10
  map[["list"]] <- list(accuracy / 10, precision / 10, recall / 10, f / 10)
  map[["all_a"]] <- all_a
  map[["all_p"]] <- all_p
  map[["all_r"]] <- all_r
  map[["all_f"]] <- all_f
  map[["list_of_10_folds"]] <- l
  return(map)
}
hepaClassification <- function(c){
  l <- list()
  accuracy <- 0
  error_rate <- 0
  precision <- 0
  recall <- 0
  f <- 0
  all_a <- list()
  all_p <- list()
  all_r <- list()
  all_f <- list()
  for(i in 1:10){
    classifier <- c(V1~., data=hepa) %>% evaluate_Weka_classifier(numFolds = 10)
    l[[i]] <- measuresMap(classifier)
    all_a[[i]] <- l[[i]][["Accuracy"]]
    all_p[[i]] <- l[[i]][["Precision"]]
    all_r[[i]] <- l[[i]][["Recall"]]
    all_f[[i]] <- l[[i]][["F-score"]]
    accuracy <- accuracy + l[[i]][["Accuracy"]]
    error_rate <- error_rate + l[[i]][["Error_rate"]]
    precision <- precision + l[[i]][["Precision"]]
    recall <- recall + l[[i]][["Recall"]]
    f <- f + l[[i]][["F-score"]]
  }
  map <- new.env(hash=T, parent=emptyenv())
  map[["Accuracy"]] <- accuracy /10
  map[["Error_rate"]] <- error_rate/10
  map[["Precision"]]  <- precision/10
  map[["Recall"]]  <- recall/10
  map[["F-score"]]  <-f/10
  map[["list"]] <- list(accuracy / 10, precision / 10, recall / 10, f / 10)
  map[["all_a"]] <- all_a
  map[["all_p"]] <- all_p
  map[["all_r"]] <- all_r
  map[["all_f"]] <- all_f
  map[["list_of_10_folds"]] <- l
  return(map)
}
spectClassification <- function(c){
  l <- list()
  accuracy <- 0
  error_rate <- 0
  precision <- 0
  recall <- 0
  f <- 0
  all_a <- list()
  all_p <- list()
  all_r <- list()
  all_f <- list()
  for(i in 1:10){
    classifier <- c(V1~., data=spect) %>% evaluate_Weka_classifier(numFolds = 10)
    l[[i]] <- measuresMap(classifier)
    all_a[[i]] <- l[[i]][["Accuracy"]]
    all_p[[i]] <- l[[i]][["Precision"]]
    all_r[[i]] <- l[[i]][["Recall"]]
    all_f[[i]] <- l[[i]][["F-score"]]
    accuracy <- accuracy + l[[i]][["Accuracy"]]
    error_rate <- error_rate + l[[i]][["Error_rate"]]
    precision <- precision + l[[i]][["Precision"]]
    recall <- recall + l[[i]][["Recall"]]
    f <- f + l[[i]][["F-score"]]
  }
  map <- new.env(hash=T, parent=emptyenv())
  map[["Accuracy"]] <- accuracy /10
  map[["Error_rate"]] <- error_rate/10
  map[["Precision"]]  <- precision/10
  map[["Recall"]]  <- recall/10
  map[["F-score"]]  <-f/10
  map[["list"]] <- list(accuracy / 10, precision / 10, recall / 10, f / 10)
  map[["all_a"]] <- all_a
  map[["all_p"]] <- all_p
  map[["all_r"]] <- all_r
  map[["all_f"]] <- all_f
  map[["list_of_10_folds"]] <- l
  return(map)
}
diabetesClassification <- function(c){
  l <- list()
  accuracy <- 0
  error_rate <- 0
  precision <- 0
  recall <- 0
  f <- 0
  all_a <- list()
  all_p <- list()
  all_r <- list()
  all_f <- list()
  for(i in 1:10){
    classifier <- c(V9~., data=diabetes) %>% evaluate_Weka_classifier(numFolds = 10)
    l[[i]] <- measuresMap(classifier)
    all_a[[i]] <- l[[i]][["Accuracy"]]
    all_p[[i]] <- l[[i]][["Precision"]]
    all_r[[i]] <- l[[i]][["Recall"]]
    all_f[[i]] <- l[[i]][["F-score"]]
    accuracy <- accuracy + l[[i]][["Accuracy"]]
    error_rate <- error_rate + l[[i]][["Error_rate"]]
    precision <- precision + l[[i]][["Precision"]]
    recall <- recall + l[[i]][["Recall"]]
    f <- f + l[[i]][["F-score"]]
  }
  map <- new.env(hash=T, parent=emptyenv())
  map[["Accuracy"]] <- accuracy / 10
  map[["Error_rate"]] <- error_rate / 10
  map[["Precision"]]  <- precision / 10
  map[["Recall"]]  <- recall / 10
  map[["F-score"]]  <-f / 10
  map[["list"]] <- list(accuracy / 10, precision / 10, recall / 10, f / 10)
  map[["all_a"]] <- all_a
  map[["all_p"]] <- all_p
  map[["all_r"]] <- all_r
  map[["all_f"]] <- all_f
  map[["list_of_10_folds"]] <- l
  return(map)
}
```

Applying C4.5 on the sonar dataset and showing the results of each fold :
```{r}
c4.5_sonar <- sonarClassification(J48)
for(d in c4.5_sonar[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying C4.5 on the hapatitis dataset and showing the results of each fold :
```{r}
c4.5_hepa <- hepaClassification(J48)
for(d in c4.5_hepa[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying C4.5 on the spect dataset and showing the results of each fold :
```{r}
c4.5_spect <- spectClassification(J48)
for(d in c4.5_spect[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying C4.5 on the diabetes dataset and showing the results of each fold :
```{r}
c4.5_diabetes <- diabetesClassification(J48)
for(d in c4.5_diabetes[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Random Forest on the sonar dataset and showing the results of each fold :
```{r}
rf_sonar <- sonarClassification(RF)
for(d in rf_sonar[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Random Forest on the hapatitis dataset and showing the results of each fold :
```{r}
rf_hepa <- hepaClassification(RF)
for(d in rf_hepa[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Random Forest on the spect dataset and showing the results of each fold :
```{r}
rf_spect <- spectClassification(RF)
for(d in rf_spect[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Random Forest on the diabetes dataset and showing the results of each fold :
```{r}
rf_diabetes <- diabetesClassification(RF)
for(d in rf_diabetes[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying SVM on the sonar dataset and showing the results of each fold :
```{r}
svm_sonar <- sonarClassification(SMO)
for(d in svm_sonar[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying SVM on the hapatitis dataset and showing the results of each fold :
```{r}
svm_hepa <- hepaClassification(SMO)
for(d in svm_hepa[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying SVM on the spect dataset and showing the results of each fold :
```{r}
svm_spect <- spectClassification(SMO)
for(d in svm_spect[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying SVM on the diabetes dataset and showing the results of each fold :
```{r}
svm_diabetes <- diabetesClassification(NB)
for(d in svm_diabetes[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Naive Bayes on the sonar dataset and showing the results of each fold :
```{r}
nb_sonar <- sonarClassification(NB)
for(d in nb_sonar[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Naive Bayes on the hapatitis dataset and showing the results of each fold :
```{r}
nb_hepa <- hepaClassification(NB)
for(d in nb_hepa[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Naive Bayes on the spect dataset and showing the results of each fold :
```{r}
nb_spect <- spectClassification(NB)
for(d in nb_spect[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Naive Bayes on the diabetes dataset and showing the results of each fold :
```{r}
nb_diabetes <- diabetesClassification(NB)
for(d in nb_diabetes[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Neural Networks on the hapatitis dataset and showing the results of each fold :
```{r}
#nn_hepa <- hepaClassification(NN)
#for(d in nn_hepa[["list_of_10_folds"]]){
 #cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
#}
```

Applying Neural Networks on the spect dataset and showing the results of each fold :
```{r}
#nn_spect <- spectClassification(NN)
#for(d in nn_spect[["list_of_10_folds"]]){
 #cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", #Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", #d[["F-score"]], "\n")
#}
```

Applying Neural Networks on the diabetes dataset and showing the results of each fold :
```{r}
#nn_diabetes <- diabetesClassification(NN)
#for(d in nn_diabetes[["list_of_10_folds"]]){
 #cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
#}
```

Applying Bagging on the sonar dataset and showing the results of each fold :
```{r}
bag_sonar <- sonarClassification(Bagging)
for(d in bag_sonar[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Bagging on the hapatitis dataset and showing the results of each fold :
```{r}
bag_hepa <- hepaClassification(Bagging)
for(d in bag_hepa[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Bagging on the spect dataset and showing the results of each fold :
```{r}
bag_spect <- spectClassification(Bagging)
for(d in bag_spect[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Bagging on the diabetes dataset and showing the results of each fold :
```{r}
bag_diabetes <- diabetesClassification(Bagging)
for(d in bag_diabetes[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Boosting on the sonar dataset and showing the results of each fold :
```{r}
boost_sonar <- sonarClassification(AdaBoostM1)
for(d in boost_sonar[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Boosting on the hapatitis dataset and showing the results of each fold :
```{r}
boost_hepa <- hepaClassification(AdaBoostM1)
for(d in boost_hepa[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Boosting on the spect dataset and showing the results of each fold :
```{r}
boost_spect <- spectClassification(AdaBoostM1)
for(d in boost_spect[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

Applying Boosting on the diabetes dataset and showing the results of each fold :
```{r}
boost_diabetes <- diabetesClassification(AdaBoostM1)
for(d in boost_diabetes[["list_of_10_folds"]]){
 cat("Accuracy = ", d[["Accuracy"]], ", Error rate = ", d[["Error_rate"]], ", Precision = ", d[["Precision"]], ", Recall = ", d[["Recall"]], ", F-score = ", d[["F-score"]], "\n")
}
```

##4.1.2 Formating the evaluation metrics:
```{r}

l = c(c4.5_sonar, rf_sonar, svm_sonar, nb_sonar, bag_sonar, boost_sonar)
a <- c()
p <- c()
r <- c()
f <- c()
for(n in l){
  a <- c(a, n[["Accuracy"]])
  p <- c(p, n[["Precision"]])
  r <- c(r, n[["Recall"]])
  f <- c(f, n[["F-score"]])
}
accuracy_matrix = matrix(data = a, nrow = 1)
precision_matrix = matrix(data = p, nrow = 1)
recall_matrix = matrix(data = r, nrow = 1)
f_score_matrix = matrix(data = f, nrow = 1) 

l = c(c4.5_hepa, rf_hepa, svm_hepa, nb_hepa, bag_hepa, boost_hepa)
a <- c()
p <- c()
r <- c()
f <- c()
for(n in l){
  a <- c(a, n[["Accuracy"]])
  p <- c(p, n[["Precision"]])
  r <- c(r, n[["Recall"]])
  f <- c(f, n[["F-score"]])
}
accuracy_matrix = rbind(accuracy_matrix, a)
precision_matrix = rbind(precision_matrix, p)
recall_matrix = rbind(recall_matrix, r)
f_score_matrix = rbind(f_score_matrix, f)

l = c(c4.5_spect, rf_spect, svm_spect, nb_spect, bag_spect, boost_spect)
a <- c()
p <-c()
r <- c()
f <- c()
for(n in l){
  a <- c(a, n[["Accuracy"]])
  p <- c(p, n[["Precision"]])
  r <- c(r, n[["Recall"]])
  f <- c(f, n[["F-score"]])
}
accuracy_matrix = rbind(accuracy_matrix, a)
precision_matrix = rbind(precision_matrix, p)
recall_matrix = rbind(recall_matrix, r)
f_score_matrix = rbind(f_score_matrix, f)

l = c(c4.5_diabetes, rf_diabetes, svm_diabetes, nb_diabetes, bag_diabetes, boost_diabetes)
a<- c()
p <-c()
r <- c()
f <- c()
for(n in l){
  a <- c(a, n[["Accuracy"]])
  p <- c(p, n[["Precision"]])
  r <- c(r, n[["Recall"]])
  f <- c(f, n[["F-score"]])
}
accuracy_matrix = rbind(accuracy_matrix, a)
precision_matrix = rbind(precision_matrix, p)
recall_matrix = rbind(recall_matrix, r)
f_score_matrix = rbind(f_score_matrix, f)

rownames(accuracy_matrix) <- c("sonar","hepa", "spect", "diabetes")
colnames(accuracy_matrix) <- c("C4.5", "RF", "SVM", "NB", "Bagging", "Boosting")
rownames(precision_matrix) <- c("sonar","hepa", "spect", "diabetes")
colnames(precision_matrix) <- c("C4.5", "RF", "SVM", "NB", "Bagging", "Boosting")
rownames(recall_matrix) <- c("sonar","hepa", "spect", "diabetes")
colnames(recall_matrix) <- c("C4.5", "RF", "SVM", "NB", "Bagging", "Boosting")
rownames(f_score_matrix) <- c("sonar","hepa", "spect", "diabetes")
colnames(f_score_matrix) <- c("C4.5", "RF", "SVM", "NB", "Bagging", "Boosting")
kable(accuracy_matrix)
kable(precision_matrix)
kable(recall_matrix)
kable(f_score_matrix)
```

##4.2 Comparison:
###In sonar dataset:
For accuracy metric we can easily notice from the accuracy matrix that Random Forest algorithm is the winner but we need to use Student’s Paired T Test to detect if the metric differences are statistically significant to do so we can apply t test on the 10 values of accuracy that we from each classifier :
```{r}
t.test(unlist(rf_sonar[["all_a"]]), unlist(svm_sonar[["all_a"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_a"]]), unlist(nb_sonar[["all_a"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_a"]]), unlist(c4.5_sonar[["all_a"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_a"]]), unlist(bag_sonar[["all_a"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_a"]]), unlist(boost_sonar[["all_a"]]), paired = TRUE)
```
Therefore we can deduce that Random Forest is the winner in sonar dataset for accuracy metric.

For precision metric we can easily notice that Random Forest algorithm is the winner by applying Paired T Test: 
```{r}
t.test(unlist(rf_sonar[["all_p"]]), unlist(svm_sonar[["all_p"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_p"]]), unlist(nb_sonar[["all_p"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_p"]]), unlist(c4.5_sonar[["all_p"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_p"]]), unlist(bag_sonar[["all_p"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_p"]]), unlist(boost_sonar[["all_p"]]), paired = TRUE)
```
Therefore we can deduce that Random Forest is the winner in sonar dataset for precision metric.

For recall metric we can easily notice that Random Forest algorithm is the winner by applying Paired T Test: 
```{r}
t.test(unlist(rf_sonar[["all_r"]]), unlist(svm_sonar[["all_r"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_r"]]), unlist(nb_sonar[["all_r"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_r"]]), unlist(c4.5_sonar[["all_r"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_r"]]), unlist(bag_sonar[["all_r"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_r"]]), unlist(boost_sonar[["all_r"]]), paired = TRUE)
```
Therefore we can deduce that Random Forest is the winner in sonar dataset for recall metric.

For f-score metric we can easily notice that Random Forest algorithm is the winner by applying Paired T Test:
```{r}
t.test(unlist(rf_sonar[["all_f"]]), unlist(svm_sonar[["all_f"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_f"]]), unlist(nb_sonar[["all_f"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_f"]]), unlist(c4.5_sonar[["all_f"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_f"]]), unlist(bag_sonar[["all_f"]]), paired = TRUE)
t.test(unlist(rf_sonar[["all_f"]]), unlist(boost_sonar[["all_f"]]), paired = TRUE)
```
Therefore we can deduce that Random Forest is the winner in sonar dataset for all metrics.
##### So we can conclude that Random forest is the winner algorithm in sonar dataset
###In hepatitis dataset:
We can notice that c4.5 is the winner for the accuracy metric by applying Paired T Test:
```{r}
t.test(unlist(c4.5_hepa[["all_a"]]), unlist(svm_hepa[["all_a"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_a"]]), unlist(nb_hepa[["all_a"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_a"]]), unlist(rf_hepa[["all_a"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_a"]]), unlist(bag_hepa[["all_a"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_a"]]), unlist(boost_hepa[["all_a"]]), paired = TRUE)
```
So we can deduce that the difference between accuracy of c4.5 and all algorithms is significant except for naive bayes

We can notice that Random Forest is the winner for the precision metric by applying Paired T Test:
```{r}
t.test(unlist(rf_hepa[["all_p"]]), unlist(svm_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(rf_hepa[["all_p"]]), unlist(nb_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(rf_hepa[["all_p"]]), unlist(c4.5_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(rf_hepa[["all_p"]]), unlist(bag_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(rf_hepa[["all_p"]]), unlist(boost_hepa[["all_p"]]), paired = TRUE)
```
results of T test cannot show the significant difference between Random Forest and other algorithms so we can try c4.5 as it's the second winner:
```{r}
t.test(unlist(c4.5_hepa[["all_p"]]), unlist(svm_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_p"]]), unlist(nb_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_p"]]), unlist(rf_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_p"]]), unlist(bag_hepa[["all_p"]]), paired = TRUE)
t.test(unlist(c4.5_hepa[["all_p"]]), unlist(boost_hepa[["all_p"]]), paired = TRUE)
```
so we can deduce the segnificant difference for all algorithms except for rf

For recall metric we can notice that Naive Bayes is the winner by applying T test:
```{r}
t.test(unlist(nb_hepa[["all_r"]]), unlist(svm_hepa[["all_r"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_r"]]), unlist(c4.5_hepa[["all_r"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_r"]]), unlist(rf_hepa[["all_r"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_r"]]), unlist(bag_hepa[["all_r"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_r"]]), unlist(boost_hepa[["all_r"]]), paired = TRUE)
```
so we can see the difference between Naive Bayes and other algorithms is signifcant

For f-score metric we can notice that Naive Bayes is the winner by applying T test:
```{r}
t.test(unlist(nb_hepa[["all_f"]]), unlist(svm_hepa[["all_f"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_f"]]), unlist(c4.5_hepa[["all_f"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_f"]]), unlist(rf_hepa[["all_f"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_f"]]), unlist(bag_hepa[["all_f"]]), paired = TRUE)
t.test(unlist(nb_hepa[["all_f"]]), unlist(boost_hepa[["all_f"]]), paired = TRUE)
```
so we can see the difference between Naive Bayes and other algorithms is signifcant
##### So we can deduce that C4.5 and Naive Bayes are similarly winning in hepatities datset
###In spect dataset:
For accuracy metric we can notice that Bagging is the winner by applying T test:
```{r}
t.test(unlist(bag_spect[["all_a"]]), unlist(svm_spect[["all_a"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_a"]]), unlist(c4.5_spect[["all_a"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_a"]]), unlist(rf_spect[["all_a"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_a"]]), unlist(nb_spect[["all_a"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_a"]]), unlist(boost_spect[["all_a"]]), paired = TRUE)
```
so the difference between bagging and other algorithms is significant except for Random Forest and SVM. 

For precision metric we can notice that Bagging is the winner by applying T test:
```{r}
t.test(unlist(bag_spect[["all_p"]]), unlist(svm_spect[["all_p"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_p"]]), unlist(c4.5_spect[["all_p"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_p"]]), unlist(rf_spect[["all_p"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_p"]]), unlist(nb_spect[["all_p"]]), paired = TRUE)
t.test(unlist(bag_spect[["all_p"]]), unlist(boost_spect[["all_p"]]), paired = TRUE)
```
so the difference between bagging and other algorithms is significant except for SVM.

For precision metric we can notice that Naive Bayes is the winner by applying T test:
```{r}
t.test(unlist(nb_spect[["all_r"]]), unlist(svm_spect[["all_r"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_r"]]), unlist(c4.5_spect[["all_r"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_r"]]), unlist(rf_spect[["all_r"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_r"]]), unlist(bag_spect[["all_r"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_r"]]), unlist(boost_spect[["all_r"]]), paired = TRUE)
```
so the difference between bagging and other algorithms is significant.

For F-score metric we can notice that Naive Bayes is the winner by applying T test:
```{r}
t.test(unlist(nb_spect[["all_f"]]), unlist(svm_spect[["all_f"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_f"]]), unlist(c4.5_spect[["all_f"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_f"]]), unlist(rf_spect[["all_f"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_f"]]), unlist(bag_spect[["all_f"]]), paired = TRUE)
t.test(unlist(nb_spect[["all_f"]]), unlist(boost_spect[["all_f"]]), paired = TRUE)
```
so the difference between bagging and other algorithms is significant.
##### So we can deduce that Naive Bayes is the winner in spect datset
###In diabetes dataset
We can notice that Random Forest is the winner for the accuracy metric by applying Paired T Test:
```{r}
t.test(unlist(rf_diabetes[["all_a"]]), unlist(svm_diabetes[["all_a"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_a"]]), unlist(nb_diabetes[["all_a"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_a"]]), unlist(c4.5_diabetes[["all_a"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_a"]]), unlist(bag_diabetes[["all_a"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_a"]]), unlist(boost_diabetes[["all_a"]]), paired = TRUE)
```
so the difference between Random Forest and other algorithms is significant except for SVM and Bagging.

We can notice that Random Forest is the winner for the precision metric by applying Paired T Test:
```{r}
t.test(unlist(rf_diabetes[["all_p"]]), unlist(svm_diabetes[["all_p"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_p"]]), unlist(nb_diabetes[["all_p"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_p"]]), unlist(c4.5_diabetes[["all_p"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_p"]]), unlist(bag_diabetes[["all_p"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_p"]]), unlist(boost_diabetes[["all_p"]]), paired = TRUE)
```
so the difference between Random Forest and other algorithms is significant except for SVM and C4.5.

We can notice that there is now winner classifier as the difference between classifiers are small so we try to calculate T test for Bagging with other classifiers
```{r}
t.test(unlist(bag_diabetes[["all_r"]]), unlist(svm_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(bag_diabetes[["all_r"]]), unlist(nb_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(bag_diabetes[["all_r"]]), unlist(c4.5_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(bag_diabetes[["all_r"]]), unlist(rf_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(bag_diabetes[["all_r"]]), unlist(boost_diabetes[["all_r"]]), paired = TRUE)
```
then we try Random forest with the other classifiers:
```{r}
t.test(unlist(rf_diabetes[["all_r"]]), unlist(svm_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_r"]]), unlist(nb_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_r"]]), unlist(c4.5_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_r"]]), unlist(bag_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_r"]]), unlist(boost_diabetes[["all_r"]]), paired = TRUE)
```
then we try Boosting :
```{r}
t.test(unlist(boost_diabetes[["all_r"]]), unlist(svm_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(boost_diabetes[["all_r"]]), unlist(nb_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(boost_diabetes[["all_r"]]), unlist(c4.5_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(boost_diabetes[["all_r"]]), unlist(bag_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(boost_diabetes[["all_r"]]), unlist(rf_diabetes[["all_r"]]), paired = TRUE)
```
then we try Naive Bayes
```{r}
t.test(unlist(svm_diabetes[["all_r"]]), unlist(nb_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(svm_diabetes[["all_r"]]), unlist(boost_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(svm_diabetes[["all_r"]]), unlist(c4.5_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(svm_diabetes[["all_r"]]), unlist(bag_diabetes[["all_r"]]), paired = TRUE)
t.test(unlist(svm_diabetes[["all_r"]]), unlist(rf_diabetes[["all_r"]]), paired = TRUE)
```
the there is now winner for recall metric

For f-score metric we can notice that Random Forest algorithm is the winner by applying Paired T Test:
```{r}
t.test(unlist(rf_diabetes[["all_f"]]), unlist(svm_diabetes[["all_f"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_f"]]), unlist(nb_diabetes[["all_f"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_f"]]), unlist(c4.5_diabetes[["all_f"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_f"]]), unlist(bag_diabetes[["all_f"]]), paired = TRUE)
t.test(unlist(rf_diabetes[["all_f"]]), unlist(boost_diabetes[["all_f"]]), paired = TRUE)
```
so we can deduce that Random Forest is the winner in sonar dataset for all except for Bagging.

####Therefore there is No algorithm which performs statistically significantly better than the other algorithms in all datasets
